a and generators

### 2022-05-06 documentos/generators.tex
No nos fuimos a duelo a muerte con cuchillos con CP

\janote{The connection between rows or columns of $a$ and single-qubit PCE
generators $\mathcal G_\alpha$ is shown; identifying -1s with 0s one is 
left with the sets $\{\tau_\alpha\}$ of preserved and erased components
by each $\mathcal G_\alpha$.
holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
\cpnote{The connection between rows or columns of $a$ and single-qubit PCE

@@

holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 

@@

>>>>

%\janote{The connection between rows or columns of $a$ and single-qubit PCE
%generators $\mathcal G_\alpha$ is shown; identifying -1s with 0s one is 
%left with the sets $\{\tau_\alpha\}$ of preserved and erased components
%by each $\mathcal G_\alpha$.
%For any number of particles, such simple relation 
%holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
%\cpnote{
The connection between rows or columns of $a$ and single-qubit PCE

@@

holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.
\janote{Propuesta de CP y JA. Le toca a la gente resolver que también 
están de acuerdo, o no}

@@

%}
